Reading Notes

### 2020-07-15 reading-notes.tex
writing for the day about what automated mapping exists
read Zhang

\cite{Cummings2019}
each research group used to maintain their own code ,but now these codes are general purpose and shared. open source aid reproducibility because (1) users can look at the source code to find bug and these can be very quickly fixed, (2) monetary cost can exclude users who can't afford it.
a disadvantage is that open source software may be less new user friendly and instead of a gui may use scripts. scripts are an advantage to reproducability however because they allow for user to show and version control exactly what they did with little to no ambiguity. GUI's may obscure the actual mehtod.
ooh I want to look at etomica. hmm. doesnt work in my browser.
overall this was a good summary of what exists but no big takeaways

>>>>

\cite{Cummings2019}

each research group used to maintain their own code ,but now these codes are general purpose and shared. open source aid reproducibility because (1) users can look at the source code to find bug and these can be very quickly fixed, (2) monetary cost can exclude users who can't afford it.
a disadvantage is that open source software may be less new user friendly and instead of a gui may use scripts. scripts are an advantage to reproducability however because they allow for user to show and version control exactly what they did with little to no ambiguity. GUI's may obscure the actual mehtod.
ooh I want to look at etomica. hmm. doesnt work in my browser.
overall this was a good summary of what exists but no big takeaways

\cite{Zhang2008}

next time read this and write about mapping operators
essential dynamics coarse-graining. replacing large and complex domains of biomolecules with relatively few CG sites. CG map variationally determined to best reflect the essential dynamics. CG model designed to explore protein conformational space.
processes tht occur on length and time sclaes far beyond simulations with atomic resolution (virus capsid assembly,etc) 
two facets -- number of CG sites and location. for lipids or peptides it is reasonable to replace each functional group with a bead. different levels of resolution for each amino acid. but when looking at HIV capsid composed of thousand of CA protein dimers each CA composed of >200 residues we need a few CG sites per dimer. actin filaments are a similar problem. 
other solutions: 
- (shape focused) rigid units defined by a topological algorithm (like a hard polygon?)  
- (movement focused) CG map that reflects collective motions determined by principle component analysis. small number of PCA modes which define essential dynamics. basically this article is about choosing sites that will best reflect the movements of a protein using math.

\cite{Cao2015a}
